---
title: "p8105_hw1_jx2562"
author: "Jingyi"
date: "2023-09-15"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
library(moderndive)
library(ggplot2)
```


# Problem 1

Here we use ggplot to scatter the correlation between _temp_ and _time_hour_, with _humid_ indicating the color of the points.

Load the libraries (**moderndive** and **ggplot**) and dataset (**early_january_weather**) we are going to use.

```{r load_data}
data("early_january_weather")
```

The dataset **early_january_weather** include `r ncol(early_january_weather)` columns and `r nrow(early_january_weather)` rows. 

The variables in the dataset includes _`r colnames(early_january_weather)`_. 

The mean of the temperature in the early january is `r mean(early_january_weather$temp)`.

```{r plot}
ggplot(data = early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point()

ggsave("temp over time.jpg")
```

It is apparent from the graph that as time pass by, the temperature grew gradually with fluctuation. In terms of humidity, it rose up and reached its summit in January 14.


# Problem 2

Here we created a dataframe including _numeric_, _boolean_, _character_, and _factor_ variables. Then, some operations were conducted on the dataframe to help us better comprehend these concepts in R. 

First, we created a dataframe containing: 
*   a random sample of size 10 from a standard Normal distribution
*   a logical vector indicating whether elements of the sample are greater than 0
*   a character vector of length 10
*   a factor vector of length 10, with 3 different factor “levels”


```{r creat_df}
df = tibble(
  std_norm = rnorm(10),
  logical_vec = std_norm > 0,
  char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  factor_vec = factor(sample(c("Low", "Medium", "High"), size = 10, replace = TRUE))
)
df
```

This below code chunk took the mean of each column and saw how it goes.
```{r get_mean}
mean_std_norm <- mean(df %>% pull(std_norm))
mean_logical <- mean(df %>% pull(logical_vec))
mean_char <- mean(df %>% pull(char_vec))
mean_factor <- mean(df %>% pull(factor_vec))
mean_std_norm
mean_logical
mean_char
mean_factor
```
We can take the mean of _numeric_ and _logical_ data, but not _character_ and _factor_ variables. Instead, an NA was introduced.

```{r convert_num}
num_logical <- as.numeric(df %>% pull(logical_vec))
num_char <- as.numeric(df %>% pull(char_vec))
num_factor <- as.numeric(df %>% pull(factor_vec))
```

Except for character variable, the other two data types can be converted to _numeric_ data. The result coincided with taking the mean except for the _factor_ variable. Factor variables were discrete labels but not numbers, so we cannot take their means. The function `mean()` will not convert the _factor_ variables and _character_ variable to _numeric_ data first. If we want to calculate the mean of factor variable, we can convert it to _numeric_ data with `as.numeric()`.


